Extending statistical models for source attribution of zoonotic diseases: A study of campylobacteriosis

### 2018-03-20 paper/finalish/article_1023.tex
updates latex document to new template from wiley

\documentclass[times, doublespace]{simauth}%For paper submission
%\documentclass[times]{simauth}
% Packages
\usepackage{mdframed}
\usepackage{subcaption}
\usepackage{subfig}
\usepackage{url}
\usepackage{color}
%\usepackage[T1]{fontenc}
%\usepackage{times}
%\usepackage{bm}
%\usepackage{mathtime}

% Customised Commands
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}
\newenvironment{proof}[1][Proof]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newcommand{\qed}{\nobreak \ifvmode \relax \else
      \ifdim\lastskip<1.5em \hskip-\lastskip
      \hskip1.5em plus0em minus0.5em \fi \nobreak
      \vrule height0.75em width0.5em depth0.25em\fi}

% Bibliographystyle
\bibliographystyle{wileyj}

\begin{document}
\runninghead{Extending statistical models for the source attribution of zoonotic diseases}
\title{Extending statistical models for source attribution of zoonotic diseases: A study of campylobacteriosis}
\author{Sih-Jing Liao\affil{a},
Jonathan Marshall\affil{a}\corrauth\footnotemark[2], Martin L. Hazelton\affil{a} and Nigel P. French\affil{b}}
\address{\affilnum{a} Institute of Fundamental Sciences-Statistics, Massey University, Palmerston North, New Zealand\\
\affilnum{b} mEpiLab, Hopkirk Research Institute, Massey University, Palmerston North, New Zealand}
\corraddr{Jonathan Marshall, Institute of Fundamental Sciences-Statistics, Massey University, Private Bag 11222, Palmerston North, New Zealand\\ \footnotemark[2] E-mail: J.C.marshall@massey.ac.nz}

\begin{abstract}

Preventing and controlling zoonoses through the design and implementation of public health policies requires a thorough understanding of transmission pathways. Modeling jointly the epidemiological data and genetic information of microbial isolates derived from cases provides a methodology for tracing back the source of infection. In this paper, the attribution probability for human cases of campylobacteriosis for each source, conditional on the extent to which each case resides in a rural compared to urban environment, is estimated. A model that incorporates genetic data and evolutionary processes is applied alongside a newly developed genetic-free model. We show that inference from each model is comparable except for rare microbial genotypes, and that the effect of ``rurality'' may be modeled linearly on the logit scale, with increasing rurality leading to increasing likelihood of ruminant-sourced campylobacteriosis.

\end{abstract}

\keywords{source attribution; \textit{Campylobacter}; genetic model; Dirichlet prior; HPD interval; DIC}
\maketitle

>>>>

\RequirePackage{etex}
\documentclass[AMA,STIX1COL]{WileyNJD-v2}

\articletype{Research Article}%

\received{26 April 2016}
\revised{6 June 2016}
\accepted{6 June 2016}

\raggedbottom

\begin{document}

\title{Extending statistical models for source attribution of zoonotic diseases: A study of campylobacteriosis}

\author[1]{Sih-Jing Liao}

\author[1]{Jonathan Marshall*}

\author[1]{Martin L. Hazelton}

\author[2]{Nigel P. French}

\authormark{Sih-Jing Liao \textsc{et al}}

\address[1]{\orgdiv{Institute of Fundamental Sciences},\orgname{Massey University}, \orgaddress{\state{Palmerston North}, \country{New Zealand}}}

\address[2]{\orgdiv{mEpiLab, Hopkirk Research Institute}, \orgname{Massey University}, \orgaddress{\state{Palmerston North}, \country{New Zealand}}}

\address[3]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}

\corres{*J Marshall, Institute of Fundamental Sciences, Massey University, Palmerston North, New Zealand. \email{J.C.marshall@massey.ac.nz}}

%\presentaddress{This is sample for present address text this is sample for present address text}

\abstract[Summary]{Preventing and controlling zoonoses through the design and implementation of public health policies requires a thorough understanding of transmission pathways. Modeling jointly the epidemiological data and genetic information of microbial isolates derived from cases provides a methodology for tracing back the source of infection. In this paper, the attribution probability for human cases of campylobacteriosis for each source, conditional on the extent to which each case resides in a rural compared to urban environment, is estimated. A model that incorporates genetic data and evolutionary processes is applied alongside a newly developed genetic-free model. We show that inference from each model is comparable except for rare microbial genotypes, and that the effect of ``rurality'' may be modeled linearly on the logit scale, with increasing rurality leading to increasing likelihood of ruminant-sourced campylobacteriosis.}

\keywords{source attribution; \textit{Campylobacter}; genetic model; Dirichlet prior; HPD interval; DIC}

\jnlcitation{\cname{%
\author{S.J. Liao}, 
\author{J. Marshall}, 
\author{M.L. Hazelton}, and 
\author{N.P. French}
\author{T. Woollings}} (\cyear{2018}), 
\ctitle{Extending statistical models for source attribution of zoonotic diseases: A study of campylobacteriosis}, \cjournal{Statistics In Medicine}.} %, \cvol{2018;00:1--6}.}

\maketitle

%\footnotetext{\textbf{Abbreviations:} ANA, anti-nuclear antibodies; APC, antigen-presenting cells; IRF, interferon regulatory factor}
